Risk Perceptions for Wearable Devices

### 2015-12-11 tex-inputs/appendixes.tex
finished rough draft

>>>>

\section{Omitted Survey Questions}
\label{sec:noquestions}
Our participants answered four additional question which are not detailed in this paper. Two questions compared smartphones to wearable devices, to investigate if participants inherently saw wearables as threatening due to its unfamiliarity. The questions were not particularly well suited for this task, and our results showed no significant difference between smartphone and wearables perceptions. The other two questions asked our participants to numerically rate the risks and benefits of common, familiar technologies versus wearables (e.g., an airplane versus a wearable). In addition to the fact that these comparisons were unsound to make, our results largely highlighted our participants' unfamiliarity with wearables or other less common devices; participants rated more familiar technologies as more beneficial or risky.
